---
output: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# arcgisviz

`{arcgisviz}` builds interactive charts with the [ArcGIS Maps SDK for
JavaScript](https://developers.arcgis.com/javascript/latest/). Charts render as
htmlwidgets, so they work in the Viewer, in Quarto, and in Shiny.

<!-- badges: start -->
<!-- badges: end -->

## Installation

``` r
pak::pak("R-ArcGIS/arcgisviz")
```

## Usage

Start with `arc_chart()` and pipe. Each `set_*()` function maps one thing.

```{r eval = FALSE}
library(arcgisviz)

arc_chart(penguins) |>
  set_type("bar") |>
  set_x(species) |>
  set_y(body_mass) |>
  set_stat("mean") |>
  set_color(species) |>
  set_labs(title = "Palmer penguins", y = "Mean body mass (g)")
```

`arc_bar()`, `arc_col()`, `arc_scatter()`, and `arc_line()` are shorthand for
the common pipelines.

```{r eval = FALSE}
arc_scatter(penguins, bill_len, bill_dep) |>
  set_color(body_mass, palette = "Blue 3")
```

A numeric column becomes a continuous gradient and a categorical one gets a
colour per value. `palette` takes any of the 521 Esri colour ramps or a vector
of R colours.

## Axes

`set_axis()` handles one axis at a time. `set_flipped()` draws bars sideways.

```{r eval = FALSE}
arc_bar(penguins, island) |>
  set_axis("y", limits = c(0, NA), integer_only = TRUE) |>
  set_flipped()
```

## Configuration

Every chart is backed by S7 classes mirroring the SDK's `WebChart` JSON. Reach
for them when you need something the `set_*()` functions do not cover.

```{r}
library(arcgisviz)

chart <- arc_bar(penguins, species)

class(chart@webchart)
chart@webchart@series[[1]]@type
```
